The Tail Risk Premium - Extension of Lottery Preference Premium

### 2025-03-11 paper.qmd
Fixed Error In Ticker Selection
Added Ticker List
Updates To Annual Graphics
Added total equal-weighted portfolios
Added V2 Screening

#### Annual Returns

@@

@@

>>>>

#### Annual Returns (Value of $100k Invested)
```{python}
from visuals import annual_ret
annual_ret()

@@

```{python}
from visuals import portfolio_skews

portfolio_skews()
```

@@

#### V2 Portfolio Positions Over Time

```{python}
from visuals import ticker_count

ticker_count()
```

#### Equal Weighted Portfolios (Baseline vs Strategy-Extension)

```{python}
from visuals import portfolio_totals

portfolio_totals()
```
